Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
edits to dean and davids acknowledgement and affiliation
edits to 5.2

\author[TNG]{P. Aram\corref{cor1}}
\ead{parham.aram@univ-amu.fr}
\author[DEEE]{D. R. Freestone}
\ead{deanrf@unimelb.edu.au} 
\author[CU]{M. Dewar}
\ead{md@bit.ly}
\author[UM]{K. Scerri}
\ead{kenneth.scerri@um.edu.mt} 
 \author[TNG]{V. Jirsa}
\ead{viktor.jirsa@univ-amu.fr}
\author[DEEE]{D. B. Grayden}
\ead{grayden@unimelb.edu.au}
\author[US]{V. Kadirkamanathan}
\ead{visakan@sheffield.ac.uk}

\address[TNG]{Theoretical Neuroscience Group, UMR 1106, Institut de Neurosciences des Systemes, 13385 Marseille, France}
\address[DEEE]{NeuroEngineering Laboratory, Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
\address[CU]{bit.ly, New York City, USA}
\address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
 \address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}

@@

In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in Eqs.~(\eqref{eq:MRA-TwoScalepair1}-\eqref{eq:MRA-TwoScalepair2coefs}). 
In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^{th}$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
\subsection{Frequency Analysis}\label{sec:freq_anal}
To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline wavelets is required and is given by (see~\ref{ap:FourierofBsplines}) 
\begin{align}      
	  \mathcal{F}(\varphi_{m}\left(r\right)) &=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu),\label{eq:MRA-Wavelettransform}
\end{align}
where $\nu$ is the spatial frequency and $i=\sqrt{-1}$. From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined. This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.
\section{State and Parameter Estimation}
The aim of this section is to describe the joint state-parameter estimation method used in this study, the expectation maximization (EM) algorithm. Here we provide a general description of the algorithm and also discuss the specific formulation for MRAIDE framework.

@@

The research reported herein was partly supported by the Brain Network Recovery Group through the James S. McDonnell Foundation and the FP7-ICT BrainScales. This research was also partly supported by the Australian Research Council (Linkage Project LP100200571). 

>>>>

\author[TNG]{P. Aram\corref{cor1}}
\ead{parham.aram@univ-amu.fr}
\author[DEEE,BI]{D. R. Freestone}
\ead{deanrf@unimelb.edu.au} 
\author[CU]{M. Dewar}
\ead{md@bit.ly}
\author[UM]{K. Scerri}
\ead{kenneth.scerri@um.edu.mt} 
 \author[TNG]{V. Jirsa}
\ead{viktor.jirsa@univ-amu.fr}
\author[DEEE,BI]{D. B. Grayden}
\ead{grayden@unimelb.edu.au}
\author[US]{V. Kadirkamanathan}
\ead{visakan@sheffield.ac.uk}

\address[TNG]{Theoretical Neuroscience Group, UMR 1106, Institut de Neurosciences des Systemes, 13385 Marseille, France}
\address[DEEE]{NeuroEngineering Laboratory, Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
\address[CU]{bit.ly, New York City, USA}
\address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
 \address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}
 \address[BI]{The Bionics Institute, East Melbourne, VIC, Australia}

@@

In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in Eqs.~(\eqref{eq:MRA-TwoScalepair1}-\eqref{eq:MRA-TwoScalepair2coefs}). 
In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^{th}$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
\subsection{Frequency Analysis}\label{sec:freq_anal}
To determine the number of basis functions required to reconstruct the field and the level of approximation in the model, $j$, the frequency response of the B-spline wavelets is required. This is given by (see~\ref{ap:FourierofBsplines}) 
\begin{align}      
	  \mathcal{F}(\varphi_{m}\left(r\right)) &=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu),\label{eq:MRA-Wavelettransform}
\end{align}
where $\nu$ is the spatial frequency and $i=\sqrt{-1}$. From Eq.~\eqref{eq:MRA-Wavelettransform}, the frequency response of the wavelets and hence the level of approximation, $j$, can be determined. In this way, we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.
\section{State and Parameter Estimation}
The aim of this section is to describe the joint state-parameter estimation method used in this study, the expectation maximization (EM) algorithm. Here we provide a general description of the algorithm and also discuss the specific formulation for MRAIDE framework.

@@

The research reported herein was partly supported by the Brain Network Recovery Group through the James S. McDonnell Foundation and the FP7-ICT BrainScales. This research was also partly supported by the Australian Research Council (Linkage Project LP100200571). The Bionics Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
